Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-01 paper_intersections.tex
Section 3 changes

On the input we consider a candidate pair provided be the initialization (top-left corner).
Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $C$ and the bulk element $B$.
There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
\begin{itemize}
    \item \textbf{IC on the boundary of $C$  and inside $B$} \\
            We find all the sides coincident with the \nface of IC on $C$ component element in which the IP lies (IP can be at node and connect more sides).
            Next, we find the component neighboring elements over the sides and push all new candidate pairs
            [component neighbor -- current bulk element] into the component queue.
            Note, that there can be more than one neighbor on a side, if the component has branches.
    \item \textbf{IC on the boundary of both $C$ and $B$} \\
            We find all the faces of bulk element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neighboring bulk elements over the faces and
            push the new candidate pairs [current component element -- bulk neighbor] into the bulk queue and [component neighbor -- bulk neighbor] into the component queue.
    \item \textbf{IC inside the component element and on the boundary of the bulk element)} \\
            We proceed as in previous case, but we push only [current component element -- bulk neighbor] candidate pairs, since there is no component neighbor.
\end{itemize}

If the candidate pair has been found already, we skip it.
We also see that the candidate pairs are of three types:
[current component element -- bulk neighbor],
[component neighbor -- current bulk element], 
[component neighbor -- bulk neighbor],
from which only the first one goes into the bulk queue, trying to cover the whole component element.

@@

Then we empty the two queues. 
We pop out new candidate pairs from the \emph{bulk queue} as long as it is not empty and for every new intersection computed, we repeat the previous part (means that we can further fill both queues).
The \emph{bulk queue} is empty when the component element is fully covered by bulk elements, or
when there is no bulk neighbor to which we can advance.
Then we can pop a new candidate pair from \emph{component prolongation queue} and process it.
When both queues are empty, all intersections of a component have been found and we start over by looking for the first intersection of another component.

\notePE{We can discuss further the covering/closing of the elements and component numbering which is not tested
thoroughly at the moment. We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3d elements).}

>>>>

On the input we consider a candidate pair provided be the initialization (top-left corner).
Now we look for new candidate pairs among the neighboring elements (the block Prolongation decide).
Therefore, we iterate over the intersection corners and further exploit their topological position on the component element $c$ and the bulk element $b$.
There are 3 possible cases (applies both for 1d-3d and 2d-3d), how the intersection might be prolonged:
\begin{itemize}
    \item \textbf{IC on the boundary of $c$  and inside $b$} \\
            We find all the sides $S$ coincident with the \nface of $c$ on which IC lies. Then we get all component
            elements $C'$ neighbouring with $c$ over any side$s\in S$. And finally, we push all pairs $(c',b)$, $c'\in C'$ 
            into the component queue.
            Note, that $c$ can have more then one neighbour component elements over the single side $s$, i.e. branches are allowed.
    \item \textbf{IC on the boundary of both $c$ and $b$} \\
            We find all the faces $F$ coincident with the \nface of $b$ on which IC lies. 
            Then we get all neighbours $B'$ through all faces in $F$ as in the previous case.
            We push pairs $(c, b')$, $b'\in B'$ into the bulk queue and pairs $(c', b')$, $c'\in C'$, $b'\in B'$ into the component queue.
    \item \textbf{IC inside of $c$ anf on the boundary of $b$)} \\
            We proceed as in previous case, and push pairs $(c, b')$, $b'\in B'$ into the bulk queue.
\end{itemize}
\noteJB{Can we just use two (not excluded) cases one for IB on boundary of $c$ second for CI on boundary of $b$ ?}

We also see that the candidate pairs are of three types: $(c, b')$, $(c', b)$, $(c',b')$
from which only the first one goes into the bulk queue, trying to cover current component element $c$ before we proceed to the next one.

When the pair is taken from either of the queues we check if the pair was computed and possibly skip it. 
To this end every component element keeps a hash of the bulk elements with which we have called the intersection test.

@@

%Then we empty the two queues. 
%We pop out new candidate pairs from the \emph{bulk queue} as long as it is not empty and for every new intersection computed, 
%we repeat the previous part (means that we can further fill both queues).
%The \emph{bulk queue} is empty when the component element is fully covered by bulk elements, or
%when there is no bulk neighbor to which we can advance.
%Then we can pop a new candidate pair from \emph{component prolongation queue} and process it.
%When both queues are empty, all intersections of a component have been found and we start over by looking for the first intersection of another component.

%\notePE{We can discuss further the covering/closing of the elements and component numbering which is not tested
%thoroughly at the moment. We can show in a figure the case in 'prolong\_meshes\_13d/prolongation\_13d\_04.msh', where actually 4 components are found (therefore bulk is defined as connected 3d elements).}
